### 2015-05-24 docs/report/context.tex
updates report benchmarks links.
Changes for context

The reason why there are two kinds of context is because there will usually be data that does not need to be passed to the Web Workers with each chain, so having a global context allows this. Additionally, the local context allows users to avoid polluting the global one with keys that are not necessary for all operations.

@@

\subsection{Implementation}
Internally the context is sent as a message to all workers to make its properties available. Two possible implementatios were possible:
\begin{itemize}
  \item Send the object directly and rely on structured cloning
  \item Serialize the object using \code{JSON.stringify} and deserialize it in the workers
\end{itemize}

@@

We created to separate benchmarks, one that sends small objects to a Web Worker and another one that sends large objects to a Web Worker. Both benchmarks compare the approaches against each other.

@@

\subsection{Conclusion}
Based on the benchmark results we decided to use \code{JSON.stringify} to serialize \code{context} objects. This involves a tradeoff as, unlike structured cloning, it does not support cyclic references. For this scenario, we believe that the performance benefit is more valuable than supporting cyclic references.

>>>>

The reason why there are two kinds of context is because there will usually be data that does not need to be passed to the Web Workers with each chain, so having a global context allows this. Additionally, the local context provides a way for developers to avoid polluting the global one with keys that are not necessary for all operations.

@@

\subsection{Implementation}
Internally the context is sent as a message to all Web Workers to make its properties available. Two possible implementatios were possible:
\begin{itemize}
  \item Sending the object directly and rely on structured cloning
  \item Serializing the object using \code{JSON.stringify} and deserialize it in the workers
\end{itemize}

@@

We created two separate benchmarks, one that sends small objects to a Web Worker and another one that sends large objects to a Web Worker. Both benchmarks compare the approaches against each other.

@@

\subsection{Conclusion}
Based on the benchmark results, we decided to use \code{JSON.stringify} to serialize \code{context} objects. This involves a tradeoff as, unlike structured cloning, it does not support cyclic references. For this scenario, we believe that the performance benefit is more valuable than supporting cyclic references.
